Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
e

\tableofcontents
\newpage
\section{Introduction}
This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019. Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.  The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}. Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property. \newline
\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{123.png}
\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
\end{figure}

@@

\paragraph{Ethical concerns in the petabyte age\newline}

@@

>>>>

\tableofcontents
\newpage
\section{Introduction}
This report depictss a research performed regarding active Danish real-estate property valuations from 2016-2019. Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.  The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}. Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property. \newline
\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{123.png}
\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
\end{figure}

@@

@@

\section{An Ethical Overview}
